Stack Safety as a Security Property

### 2020-06-03 main.tex
More words in eager properties

A system satisfies integrity with respect to a callmap \(\callmap\) if
for any initial state \(\mach_0\), call state \(\mach_c\) where
\(\callmap(\mach_c) = n\), and policy state \(\pol_c\), and return
state \(\mpstate{\mach_r,\pol_r}\), where: \leo{words: induced trace, call in the trace, take the prefix}
%
\[\mach_0,\mathit{pinit}(\mach_0) \hookrightarrow ... \mpstate{\mach_c}{\pol_c,\_} ... \mpstate{\mach_r}{\pol_r,\_} | \ret{\mach_c}\]
%
it is always the case that: \leo{words here too: the value of confidential components is unchanged}
\[\forall \component . \contour(\component) = \HIGHINT \rightarrow \mach_c(\component) = \mach_r(\component)\]

@@

A system enjoys eager stack confidentiality with respect to a callmap
\(\callmap\) if, for any initial state \(\mach_0\) and call state
\(\mach_c\) such that
\(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}
\hookrightarrow ... \mpstate{\mach_c}{\pol_c,\_} ...\) and
\(\callmap(\mach_c) = n\):

      \begin{itemize}
        \item Let \(\contour = \mathit{Cof}(\mach_c,n)\)
        \item For all \(\mach_c'\) such that \(\mach_c \approx_\contour \mach_c'\):
        \item If \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P \MPT (\mach_r,p_r,\_) | \ret{\mach_c}\)
          \begin{itemize}
            \item Then there is some \(\mach_r'\) where

              \(\mach_c' \hookrightarrow \machT' (\mach_r',_) | \ret{\mach_c'}\)
            \item \(\mathit{Obs}(\MPT) \simeq \mathit{Obs}(\machT')\)
            \item And for all \(\component\), if \(\mach_c(\component) \not = \mach_r(\component)\) or
              \(\mach_c'(\component) \not = \mach_r'(\component)\), \(\mach_r(\component) = \mach_r'(\component)\)
          \end{itemize}
        \item Else, for \(\MPT\) and \(\machT'\) such that \(\mpstate{\mach_c}{\pol_c} \hookrightarrow \MPT\)
          and \(\mach_c' \hookrightarrow \machT'\), \(\MPT \sim_P \machT'\)
      \end{itemize}

>>>>

A system satisfies integrity with respect to a callmap \(\callmap\)
if for any initial mpstate \(\mpstatename =
\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\) and each call state
\(\mpostate{\mach_c}{\pol_c}{\_}\) in the induced trace from \(\mpstatename\)
where \(\callmap(\mach_c) = n\), if we take the prefix from
\(\mpstate{\mach_c}{\pol_c}\) until \(\ret{\mach_c}\) holds on some
\(\mach_p\), \(\mach_p\) matches \(\mach_c\) on each component whose integrity
in \(\mathit{Cof}(\mach_c,n)\) is \(\HIGHINT\).

@@

A system enjoys eager stack confidentiality with respect to a callmap
\(\callmap\) if, for any initial state \(\mpstatename =
\mpstate{\mach_0}{\mathit{pinit}(\mach_0,cm)}\), for each call state
\(\mpostate{\mach_c}{\pol_c}{\_}\) in the induced trace from \(\mpstatename\)
where \(\callmap(\mach_c) = n\) and each variant \(\mach_c'\) such that
\(\mach_c \approx_\contour \mach_c'\) for \(\contour = Cof(\mach_c, n)\),
one of two cases holds.

If the trace from the call reaches a return -- \(\mpstate{\mach_c}{\pol_c}
\hookrightarrow_P \MPT \mpostate{\mach_r}{\pol_r}{\_} | \ret{\mach_c}\) --
then the trace from the variant \(\mach_c'\) reaches a return --
\(\mach_c' \hookrightarrow \machT (\mach_r',\_) | \ret{\mach_c}\).
\(\MPT\) and \(\machT\) are observationally equivalent, \(\pi_o(\MPT) \eqsim
\pi_o(\machT)\). For any component \(\component\) that changed between
\(\mach_c\) and \(\mach_r\), or between \(\mach_c'\) and \(\mach_r'\),
\(\mach_r\) agrees with \(\mach_r'\) on \(\component\).

If the trace from the call never reaches a return, neither does the
trace from the variant. Then if \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P
\MPT\) and \(\mach_c' \hookrightarrow \machT\), \(\MPT \sim_P \machT\).
